### 2014-02-28 paper/formal.tex

In this section we present the formal security guarantees provided by
our embedding.
%
Concretely, we show that an IFC langauge, |specLang alpha (targetLang
nop)|, satisfies non-interference(NI)~\tocite{}.
%
Intuitively, non-interference states that secret values cannot be
leaked by programs written in the language.
%
As we show below, the precise scheduling policy |alpha| dictates
whether or not the guarantee holds for programs with diverging tasks.

We prove non-interference for |specLang alpha (targetLang nop)| using
the \emph{term erasure} technique of~\tocite{}.
%
Intuitively the term erasure technique allows us to show that a an
attacker does not learn any sensitive information from a program
written in a NI language, if the program behaves identically to the
same program with all sensitive data ``erased.''
% 
To accommodate for this, we extend our formalism to account for
programs with erased configurations and a function |erasef l| that
performs erasures, usually by rewriting (parts of) configurations that
are more sensitive than |l| to a new syntactic construct |bullet|.
%
Directly, we can now give a precise definition for the kinds of
languages we wish to prove NI.

@@

%{
%format .->  = "\overset{\alpha}{\hookrightarrow}"
Using this definition, |specLang alpha (targetLang nop) = (ifc C, ifc
V, .->, erasef il)|, such that $|ifc C| = |iS| \times \prod |it|$ and
$|ifc V| = |iS| \times |it|^*$, where $|it|^* \subset |it|$ it the
type for tasks whose expressions have been reduced to
values.\footnote{
  Here, we abuse notation by describing types for configuration parts using the
  same metavariables as the ``instance'' of the type, e.g., |it| for the type of
  task.
}
The erased configuration |tyerase (ifc C)| extends |ifc C| with configurations
containing |bullet|; Figure~\ref{fig:erasure} gives the precise definition for
our erasure function.
%
A task and its corresponding message queue is completely removed from the task
list if its label does not flow to the attacker observation level |il|;
otherwise, we apply the erasure function homomorphically and remove any message
from the task's message queue that are more sensitive than |il|.
%}

@@

Intuitively, we can now state that a language satisfies non-interference if an
attacker at level |l| cannot distinguish the runs of any two |l|-equivalent
configurations.
%
This precise NI property is called termination sensitive non-interference
(TSNI), since it considers runs of programs, and thus does not allow for leaks
due termination or internal timing behavior.
%
Formally, we define TSNI as follows.

@@

\begin{theorem}[Concurrent specification language is TSNI].
  \label{thm:rr-tsni}
For any target language |targetLang nop|, |specLang roundrobinf
(targetLang nop)| satisfies TSNI.
\end{theorem}

@@

In certain cases, however, a TSNI-safe concurrent scheduling policy such as
|roundrobinf| cannot be considered without imposig a non-trivial burden on the
concrete implementation.
%
(Section~\ref{ref:real} describes a particular embedding with JavsScript as the
target language.)
%
Hence, we consider an alternative NI property---called termination insensitive
non-interference---that can also be upheld by sequential languages at the cost
of leaking one bit through (non)-termination.
%
\begin{definition}[Termination Insensitive Non-Interference (TINI)]
  A language |(C, V, .->, erasef l)| is termination
  insensitive non-interfering if for any label |l|, and configurations
  |c1, c2 member C| and |c1', c2' member V| if
   $|c1| \approx_{|l|} |c2|$,
   $|c1| |.->|^* |c1'|$, and
   $|c2| |.->|^* |c2'|$, then
   $|c1'| \approx_{|l|} |c2'|$.
\end{definition}

>>>>

In this section we present the formal security guarantees provided by
our embedding.
%
Concretely, we show that an IFC langauge, |specLang alpha targetLang)|, satisfies non-interference~\tocite{}, without making any reference to properties of |targetLang|.
%
As it turns out, the precise scheduling policy |alpha| dictates
whether or not the guarantee holds for programs with diverging tasks.
For a sequential scheduler, we will only be able to show
\emph{termination-insensitive non-interference}, where a program
may diverge based on secret data; with the concurrent schedule,
we can show a stronger result, \emph{termination-sensitive non-interference},
where termination attacks cannot leak information.

How does one characterize what the \emph{secret inputs} of a program
are?  Like other work,~\tocite{} we show specify and prove
noninterference using \emph{term erasure}.
%
Intuitively, term erasure allows us to show that a an
attacker does not learn any sensitive information from a program
written in a non-interference language, if the program behaves identically to the
same program with all sensitive data ``erased.''
%
To accommodate for this, we extend our formalism to account for
programs with erased configurations and a function |erasef l| that
performs erasures, usually by rewriting (parts of) configurations that
are more sensitive than |l| to a new syntactic construct |bullet|.
%
We can generally characterize what features a language must have
in order for the statement of non-interference to be well-posed:

@@

%{
%format .->  = "\overset{\alpha}{\hookrightarrow}"
In our case, |specLang alpha (targetLang nop) = (ifc C, ifc
V, .->, erasef il)|, such that $|ifc C| = |iS| \times \prod |it|$ and
$|ifc V| = |iS| \times |it|_V$, where $|it|_V \subset |it|$ is the
type for tasks whose expressions have been reduced to
values.\footnote{
  Here, we abuse notation by describing types for configuration parts using the
  same metavariables as the ``instance'' of the type, e.g., |it| for the type of
  task.
}
The erased configuration |tyerase (ifc C)| extends |ifc C| with configurations
containing |bullet|; Figure~\ref{fig:erasure} gives the precise definition for
our erasure function.
%
A task and its corresponding message queue is completely removed from the task
list if its label does not flow to the attacker observation level |il|;
otherwise, we apply the erasure function homomorphically and remove any message
from the task's message queue that are more sensitive than |il|.
%}

@@

Intuitively, we can now state that a language satisfies non-interference if an
attacker at level |l| cannot distinguish the runs of any two |l|-equivalent
configurations.
%
This precise non-interference property is called termination sensitive non-interference
(TSNI), since it considers runs of programs, and thus does not allow for leaks
due termination or internal timing behavior.
%
Formally, we define TSNI as follows.

@@

\begin{theorem}[Concurrent specification language is TSNI]
  \label{thm:rr-tsni}
For any target language |targetLang nop|, |specLang roundrobinf
(targetLang nop)| satisfies TSNI.
\end{theorem}

@@

In certain cases, however, a TSNI-safe concurrent scheduling policy such as
|roundrobinf| cannot be considered without imposig a non-trivial burden on the
concrete implementation.
%
(Section~\ref{ref:real} describes a particular embedding with JavsScript as the
target language.)
%
Hence, we consider an alternative non-interference property---called termination insensitive
non-interference---that can also be upheld by sequential languages at the cost
of leaking one bit through (non)-termination.
%
\begin{definition}[Termination Insensitive Non-Interference (TINI)]
  A language |(C, V, .->, erasef l)| is termination
  insensitive non-interfering if for any label |l|, and configurations
  |c1, c2 member C| and |c1', c2' member V| if
   $|c1| \approx_{|l|} |c2|$,
   $|c1| |.->|^* |c1'|$, and
   $|c2| |.->|^* |c2'|$, then
   $|c1'| \approx_{|l|} |c2'|$.
\end{definition}
